### 2016-09-22 results.tex

\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al. in~\cite{xxx}. Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

@@

\begin{theorem}\label{thm:lin-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B} + \mbox{[TBD]}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}[Proof (sketch). ]
\end{proof}

>>>>

\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked
by Neidermayer et al. in~\cite{xxx}. \todo{Not actually a true
  statement, because $\Rep$ isn't correct.  Needs fixing.} Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

@@

\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Should follow from Jon's general result(?)}

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
\heading{Bigram Linear-PRF construction (``Neidermayer''). }
\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}

Next we consider the privacy of this construction, relative to a leakage function that behaves as follows.  On input a set $S=\{x_1,x_2,\ldots,x_n\}$, it computes $B_i \gets \mathsf{bigram}(x_i)$ for each $i \in [n]$.  Then, for all $1 \leq c \leq p$, and all size-$c$ subsets $\{j_1,j_2,\ldots,j_c\} \subseteq p$, it computes $L{j_1,j_2,\ldots,j_c}=|B_{j_1} \cap B_{j_2} \cap \ldots \cap B_{j_c}|$.  That is, it computes all of the $c$-way intersections. It returns $|S|=n$ and all of the $2^p -1$ intersection sizes as the leakage. \todo{Explain why this is plausibly leaked by $\pubaux$ for this construction.} \tsnote{This is exponential in size, so that means a simulator that reads the entire leakage will also be exponential-time in~$p$.  } \tsnote{Should we be considering smaller, but less realistic leakage, like $\mathsf{leak}(S)=S\setminus\{x\}$.}

\begin{theorem}\label{thm:bi-lin-ss}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}.  Let $\leak(S)$ be as just described.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} \mbox{[TBD]}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}[Proof (sketch). ] Adversary~$B_1^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{bi-lin}}}{A}$, using its oracle to simulate~$\Rep(S)$.  Specificially, to compute each $M_x$ index~$i$, it computes $i \gets f(b)+j\cdot F_{K_2}(b) \bmod m$ for a key~$K_2$ that it chooses.  When~$f=F_{K_1}$ then the simulation is perfect.  When~$f=\rho_1$ for a random function~$\rho_1$, then~$B_1$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{bi-lin}}}{A}$ where $\overline{\Rep}$ computes $i \gets \rho_1(b)+j\cdot F_{K_2}(b) \bmod m$.  Adversary $B_2^{g}$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{bi-lin}}}{A}$, using it's oracle to compute $i \gets \rho_1(b) + j\cdot g(b) \bmod m$, where $\rho_1$ is a (lazily sampled) random function.  When $g=F_{K_2}$ the simulation is perfect; when $g=\rho_2$ is a random function, adversary~$B_2$ simulates $\ExpPrivSSreal{\widetilde{\Pi}_{\mathrm{bi-lin}}}{A}$, where $\widetilde{\Rep}$ computes $i \gets \rho_1(b)+j\cdot\rho_2(b) \bmod m$.

Our simulator $\Sim$ receives the leakage $\leak(S)$ described earlier.  With this, it simulates $\widetilde{\Rep}$ as follows.

But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.  Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
\end{proof}
